Variational Monte Carlo on bosonic systems

### 2018-03-24 project_1/article/article.tex
Importance sampling convergence results.

	Next we will introduce importance sampling.

>>>>

	Next we will introduce importance sampling, the first prediction for importance sampling compared to 
	brute, naïve method is that we should approach an equilibrium much faster because we are now
	making moves in a smarter way. This prediction is confirmed in \autoref{fig:problem_c1} and 
	\autoref{fig:problem_c2}.

	\begin{figure}
		\centering
			\includegraphics[width=250px]{../data/figures/problem_c1.pdf}
			\caption{As the number of Monte Carlo cycles increases the standard deviation of the local energies 
			decrease. This effect is stronger when the importance sampling scheme is employed.}
			\label{fig:problem_c1}
	\end{figure}

	\begin{figure}
		\centering
			\includegraphics[width=250px]{../data/figures/problem_c2.pdf}
			\caption{The absolute difference between the expected energy and the exact energy for both brute force
			and importance sampling. }
			\label{fig:problem_c2}
	\end{figure}

	\autoref{fig:problem_c1} shows the standard deviation of the local energies for increasing number of Monte
	Carlo cycles for both the regular sampling and the importance sampling methods. We see that the standard 
	deviation decreases for both methods for a larger number of Monte Carlo cycles, but the standard deviation
	is always lower for the importance sampling method. This is in accordance with our expectations.

	We have also compared the expected energy with the exact energy for different number of Monte Carlo
	cycles. The result of this analysis is shown in \autoref{fig:problem_c2}. We see that both methods will  evnetually 
	result in expected energies that are equal to the exact energies as $\abs{E - \expval{E}} \to 0$. However, for the 
	method of importance sampling the error is consistently lower.
